Online {\IterComp}

### 2017-11-15 work.tex
removed fixme. Also setup

    We selected the work contribution of each instruction type so that total work becomes an estimator of the runtime of the unoptimized
    program.
    %Our choice to associate work with unoptimized runtime is largely arbitrary but instinctively reasonable.
    Our choice to associate work with unoptimized runtime is largely for practical reasons but it is also instinctively reasonable.
    Unoptimized time is
    close to how the programmer understands the effort put by the computer. Using it as the work metric makes work efficiency (work per unit
    of time) an estimator of the speedup of the optimized version over the unoptimized version. While other ways of setting the instruction
    contributions might be better, our results in Section~\ref{sec:results} show that this simple definition of work produces good results.
    Using the experimental setup described in Section~\ref{sec:setup}, we run the unoptimized versions of the \FIXME{7} benchmarks listed
    in \FIXME{XXX} with all 1,000 available inputs. For each run, we recorded execution time and dynamic counters for all instruction types\footnote{
    Dynamic instruction counts were obtained by using the classic block-frequency profiling.}.
    Similarly to prior work~\cite{giusto01,powell09,brandolese11}, we then applied linear regression to find the contribution of each
    instruction type that minimizes the error between measured runtime and work.
    %\footnote{The resulting regression model uses \FIXME{70}
    %different instruction types which make it too long to present here.}

@@

    Figure~\ref{fig:work-vs-O0time} shows the correlation of the work metric ($\Delta W$) with runtime for the unoptimized version of one
    benchmark that was not used for training the linear model, \texttt{susan\_c}. Each point represents the execution of a single input
    from a total of 1,000 inputs. The correlation coefficient is $0.99$, and the mean absolute percentage error (MAPE) is only about 3.5\%.
    \FIXME{More benchmarks and only coefficients?}.

>>>>

    We selected the work contribution of each instruction type so that total work becomes an estimator of the runtime of the unoptimized
    program.
    %Our choice to associate work with unoptimized runtime is largely arbitrary but instinctively reasonable.
    Our choice to associate work with unoptimized runtime is largely for practical reasons but it is also instinctively reasonable.
    Unoptimized time is
    close to how the programmer understands the effort put by the computer. Using it as the work metric makes work efficiency (work per unit
    of time) an estimator of the speedup of the optimized version over the unoptimized version. While other ways of setting the instruction
    contributions might be better, our results in Section~\ref{sec:results} show that this simple definition of work produces good results.
    Using the experimental setup described in Section~\ref{sec:setup}, we run the unoptimized versions of the 10 benchmarks listed in
    Table~\ref{tab:kdatasets:training} with all 1,000 available inputs. For each run, we recorded execution time and dynamic counters for all instruction types\footnote{
    Dynamic instruction counts were obtained by using the classic block-frequency profiling.}.
    Similarly to prior work~\cite{giusto01,powell09,brandolese11}, we then applied linear regression to find the contribution of each
    instruction type that minimizes the error between measured runtime and work.
    %\footnote{The resulting regression model uses \FIXME{70}
    %different instruction types which make it too long to present here.}

@@

    Figure~\ref{fig:work-vs-O0time} shows the correlation coefficient between the work metric ($\Delta W$) and the runtime of the
    unoptimized version for 14 benchmarks that were not used for training the linear model. The work metric correlates very strongly with
    runtime for almost all the benchmarks, the correlation coefficient being typically higher than $0.98$. The exception is the benchmarks
    based on \texttt{tiff}. The coefficient for them ranges from $0.47$ to $0.96$. Despite that, in most cases work is an excellent proxy
    for unoptimized runtime. For the rest, our Section~\ref{sec:results} evaluation shows that our work metric is still useful for quantifying
    performance.
